Target for the data

### 2023-01-16 build/code/exploration/data_structure.Rmd
first try to get extinctions from terr data

```{r cars}
reg1 <- lm(pop ~ city_fe + year_fe + treat*post + controls)
```

@@

Something like that may get the job done, but it seems computationally intensive and unelegant. Mathematically, what am I trying to do? I'm not trying to map lineage-year observations to rulers. I'm

Maybe do a function, or a dictionary. You input a terr_id and a year. It filters the rulers data down to the terr_id. Then it drops all rulers with reigns ending before or starting after that year. it returns the ruler of that lineage of that year.

Then `map` year-lineage entries to rulers with that function.

>>>>

```{r cars}
reg1 <- lm(pop ~ city_fe + year_fe + treat*post + treat*post*channel + controls)
```

In the end, `treat`x`post` will be 1 for all city-years after that city's extinction year. That's my intuition. But I haven't read up about staggered diff-in-diff yet.

@@

I did something like that in `RulersToTerritoryYears.R`. Surprisingly, only about one-third of territory-year observation have a corresponding ruler who was alive at the time. But I don't think that should be an issue. I should look at some descriptive stats.

```{r descriptive stats of rulers_linked}
rulers <- read.csv("build/temp/rulers_linked.csv")
print(rulers %>% group_by(terr_id) %>% summarise(years = n()) %>% summary())

```
The median dynasty in my data lasted 106 years. That seems plausible.

```{r more descriptive stats}
print(rulers %>% group_by(year) %>% summarise(territories = n()) %>% summary())
```
If I did it right, this means that there were on average 75 dynasties with rulers coexisting in the same year. Also plausible.

It would be interesting why the other 100,000 dynasty-year observations fell through.
Is it that some years (e.g. early years) are often missing rulers?
Is it that some dynasties (e.g. small ones) are often missing rulers?
Could there be an explanation other than data quality?
This is a potential source of bias; I should address it. Maybe limit the analysis to cities in territories larger than a certain threshold, and to recent centuries in which there are few missing links.

One more note: `rulers_linked.csv` essentially contains the personal history of all these dynasties. It contains the extinction events and, crucially, the last ruler of that dynasty, whose characteristics I can link to the event from elsewhere.
#
